Verified Time Balancing of Security Protocols \\ \large A Case Study

### 2018-12-19 Src/paper.tex
More progress formalising DH exchange

  \item Let $p$ represent the message preamble $0x505a$ followed

@@

   $alice_0(p,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$

@@

   $bob_0(p_{a0},v_{a0},c_{a0},h3_{a0},z_{a0},fs_{a0},hc_{a0}

@@

  $bob_1(p)$

@@

  $alice_1(p_{b1})$

@@

  $bob_2(p,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$

@@

   $alice_2(p_{b2},v_{b2},c_{b2},h3_{b2},z_{b2},fs_{b2},hc_{a0}

@@

  $alice_3(p)$

@@

  $bob_3(p_{a3})$

@@

  \subsection{Bob sends a Commit to Alice}
  $bob_4(p,h2,z,ha,ca,at,kt,st,hvi,m)$
  \subsection{Alice receives Bob's Commit}
  $alice_4(p_{b4},h2_{b4},z_{b4},ha_{b4},ca_{b4},at_{b4},kt_{b4}
    ,st_{b4},hvi_{b4},m_{b4})$
  \section{The DH Part 1 Message}

@@

    \item Let $asr = m(aux,rh3)$ represent the non-invertible hash

@@

  \section{The DH Part 2 Message}
  \begin{itemize}
    \item Let $istr$ represent a message denoting ``Initiator''.
    \item Let $s1$ represent the initiators first shared secret if
          it exists or null otherwise.
    \item Let $s2$ represent the initiators second shared secret if
          it exists or null otherwise.
    \item Let $rs1 = m(s1,istr)$ represent the non-invertible hash 
          of the initiators first retained shared secret.
    \item Let $rs2 = m(s2,istr)$ represent the non-invertible hash
          of the intiators second retained shared secret.
    \item Let $aux$ represet the auxiliary shared secret.
    \item Let $ih3$ represent the initiators H3 value.
    \item Let $asi = m(aux,ih3)$ represent the non-invertible hash
          of the initiators auxiliary shared secret.
    \item Let $pbx$ represent the pbx shared secret.
    \item Let $psi = m(pbx,istr)$ represent the non-invertible
          hash of the initiators pbx shared secret.

>>>>

  \item Let $pr$ represent the message preamble $0x505a$ followed

@@

   $alice_0(pr,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$

@@

   $bob_0(pr_{a0},v_{a0},c_{a0},h3_{a0},z_{a0},fs_{a0},hc_{a0}

@@

  $bob_1(pr)$

@@

  $alice_1(pr_{b1})$

@@

  $bob_2(pr,v,c,h3,z,fs,hc,cc,ac,kc,sc,hs,cs,as,ks,ss,m)$

@@

   $alice_2(pr_{b2},v_{b2},c_{b2},h3_{b2},z_{b2},fs_{b2},hc_{a0}

@@

  $alice_3(pr)$

@@

  $bob_3(pr_{a3})$

@@

  \subsection*{Bob prepares a DH Part 2 Message}
  $bob_4(pr,h1,rs1i,rs2i,asi,psi,pvi,m)$
  \subsection*{Bob sends a Commit to Alice}
  $bob_5(pr,h2,z,ha,ca,at,kt,st,hvi,m)$
  \subsection*{Alice receives Bob's Commit}
  $alice_4(pr_{b5},h2_{b5},z_{b5},ha_{b5},ca_{b5},at_{b5},kt_{b5}
    ,st_{b5},hvi_{b5},m_{b5})$
  \section*{The DH Part 1 Message}

@@

    \item Let $asr = m(auxr,rh3)$ represent the non-invertible hash

@@

  \subsection*{Alice sends DH Part 1 to Bob}
  $alice_5=(pr,h1,rs1r,rs2r,asr,psr,pvr,m)$
  \subsection*{Bob receives Alice's DH Part 1}
  $bob_6=(pr_{a5},h1_{a5},rs1r_{a5},rs2r_{a5},asr_{a5},psr_{a5},
           pvr_{a5},m_{a5})$
  \subsection*{Bob checks Alice's DH Part 1 and calculates DH 
               Result}
    \item if $pvr_{a5} = p_{b5}$ or $pvr_{a5} = p_{b5} - 1$ then 
          terminate protocol. Otherwise continue:
    \item Let $dhr = mod(pvr_{a5}^{svi_{b5}},p)$ represent the 
          DH result.
  \section*{The DH Part 2 Message}
    \item Let $istr$ represent a message denoting ``Initiator''.
    \item Let $s1$ represent the initiators first shared secret if
          it exists or null otherwise.
    \item Let $s2$ represent the initiators second shared secret if
          it exists or null otherwise.
    \item Let $rs1i = m(s1,istr)$ represent the non-invertible hash 
          of the initiators first retained shared secret.
    \item Let $rs2i = m(s2,istr)$ represent the non-invertible hash
          of the intiators second retained shared secret.
    \item Let $auxi$ represet the auxiliary shared secret.
    \item Let $ih3$ represent the initiators H3 value.
    \item Let $asi = m(auxi,ih3)$ represent the non-invertible hash
          of the initiators auxiliary shared secret.
    \item Let $pbxi$ represent the pbx shared secret.
    \item Let $psi = m(pbx,istr)$ represent the non-invertible
          hash of the initiators pbx shared secret.
  \subsection{Bob sends DH Part 2 to Alice}
  $bob_7 = bob_4$
  \subsubsection{Alice receives Bob's DH Part 2}
  $alice_6(pr_{b7},h1_{b7},rs1i_{b7},rs2i_{b7},asi_{b7},
           psi_{b7},pvi_{b7},m_{b7})$
  \subsection*{Alice checks Bob's DH Part 2 and calculates DH 
               Result}
    \item if $pvi_{b7} = p_{a5}$ or $pvr_{b7} = p_{a5} - 1$ then 
          terminate protocol. Otherwise continue:
    \item if $hash(bob_7 || alice_0) \neq hvi_b5$ then terminate 
          protocol. Otherwise continue:
    \item Let $dhr = mod(pvr_{b7}^{svi_{a5}},p)$ represent the 
          DH result.
